Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics

### 2020-04-20 Paper/main.tex
Added abstract section

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
% Provide a summary of the session. What was done, what measurements were taken,
% brief methods, what calculations, brief conclusion.  The Abstract should be
% approximately 250 words or fewer, italicized, in 10-point Times (or Times
% Roman.) Please leave two spaces between the Abstract and the heading of your
% first section.  It should briefly summarize the essence of the paper and address
% the following areas without using specific subsection titles. Objective: Briefly
% state the problem or issue addressed, in language accessible to a general
% scientific audience. Technology or Method: Briefly summarize the technological
% innovation or method used to address the problem. Results: Provide a brief
% summary of the results and findings. Conclusions: Give brief concluding remarks
% on your outcomes. Detailed discussion of these aspects should be provided in the
% main body of the paper.
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
% Provide a summary of the session. What was done, what measurements were taken,
% brief methods, what calculations, brief conclusion.  The Abstract should be
% approximately 250 words or fewer, italicized, in 10-point Times (or Times
% Roman.) Please leave two spaces between the Abstract and the heading of your
% first section.  It should briefly summarize the essence of the paper and address
% the following areas without using specific subsection titles. Objective: Briefly
% state the problem or issue addressed, in language accessible to a general
% scientific audience. Technology or Method: Briefly summarize the technological
% innovation or method used to address the problem. Results: Provide a brief
% summary of the results and findings. Conclusions: Give brief concluding remarks
% on your outcomes. Detailed discussion of these aspects should be provided in the
% main body of the paper.
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation. The random
  walk consists of a walker making steps in random directions, with each step
  having a probability of causing the walker to die and the random walk to end,
  with the probability determined by a function of position. The function can be
  chosen to model specific quantum systems. The rate of death of the walkers is
  used to calculate the ground state energy.

  This paper explores the efficacy of such a method in reproducing the known
  ground state energy of an infinite square well, and the extensibility of the
  method to more complex systems. We found that this method is very good at
  reproducing the known results to a high precision, and with good reliability,
  having very small variance in repeats. The method is extensible to higher
  dimensions, with a linear increase in time-complexity for each added dimension.
\end{abstract}
